A Monte Carlo Synthetic-Acceleration Method for Solving the Thermal Radiation Diffusion Equation\tnoteref{ornl-cr}

### 2012-09-13 doc/jcomp2012/jcomp2012.tex

  \title{A Monte Carlo Synthetic-Acceleration Method for Solving the
    Thermal Radiation Diffusion Equation}

  \author[ornl]{Thomas M. Evans\corref{cor1}\fnref{fn1}}
  \ead{evanstm@ornlgov} \ead[url]{www.ornl.gov}
  \cortext[cor1]{Corresponding Author}

@@

  \author[wisc]{Stuart R. Slattery\fnref{fn2}}
  \ead{sslattery@wisc.edu} \ead[url]{www.wisc.edu}

@@

>>>>

  \title{A Monte Carlo Synthetic-Acceleration Method for Solving the Thermal
    Radiation Diffusion Equation\tnoteref{ornl-cr}}
  \tnotetext[ornl-cr]{Notice: This manuscript has been authored by
    UT-Battelle, LLC, under contract DE-AC05-00OR22725 with the
    U.S. Department of Energy. The United States Government retains and the
    publisher, by accepting the article for publication, acknowledges that the
    United States Government retains a non-exclusive, paid-up, irrevocable,
    world-wide license to publish or reproduce the published form of this
    manuscript, or allow others to do so, for United States Government
    purposes.}

  \author[ornl]{Thomas M. Evans\corref{cor1}\fnref{fn1}} \ead{evanstm@ornlgov}
  \cortext[cor1]{Corresponding Author}

@@

  \author[wisc]{Stuart R. Slattery\fnref{fn2}} \ead{sslattery@wisc.edu}

@@

%%---------------------------------------------------------------------------%%
\section*{Acknowledgements}

Work for this paper was supported by Oak Ridge National Laboratory, which is
managed and operated by UT-Batelle, LLC, for the U.S. Department of Energy under
Contract No. DEAC05-00OR22725.
